---
title: "Share of Community-led Facilities"
output: 
  html_document:
    toc: true
    toc_float: true
date: '2022-07-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, fig.dim = c(8, 6),dpi=300)

library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(ggtext) # Improved Text Rendering Support for 'ggplot2'
library(pander) # An R 'Pandoc' Writer
```

```{r prep_data}
# filter by Local Board and service delivery model, then plot coordinates for the visual
choose_facilities <- function(local_board) {
  facilities |> 
    filter(local_board == {{local_board}}) |> 
    arrange(name) |> 
    mutate(coord_x = (row_number()-1) %% 6, coord_y = floor((row_number()/6)-0.1))
}

# count the number of facilities per Local Board and service delivery model
count_facilities <- function(local_board, delivery_model) {
  facilities |> 
    count(local_board, delivery_model) |> 
    filter(local_board == {{local_board}} & delivery_model == {{delivery_model}}) |> 
    pull(n)
}

# create the visual, showing each facility as a coloured block
build_block_visual <- function(facilities_blocks) {
  cols <- c("council led" = "#007CB9", "community led" = "#6E963C")
  community_count <- count_facilities(facilities_blocks$local_board[[1]], "community led")
  council_count <- count_facilities(facilities_blocks$local_board[[1]], "council led")
  
  ggplot(data = facilities_blocks, aes(x = coord_x, y = -coord_y)) +
    geom_point(aes(colour = delivery_model),shape=15,size=28) +
    geom_text(aes(label = stringr::str_wrap(name, 13)), colour = "white", size = 2.7, fontface = "bold") +
    scale_x_continuous(limits = c(-0.5,6.5)) +
    scale_y_continuous(limits = c(-5.5,0.25)) +
    scale_colour_manual(values = cols) +
    theme_void() +
    ggtitle(paste0("There are ", community_count, " <span style='color:", cols[["community led"]], "'><strong>community-led</strong></span> facilities and ", council_count, " <span style='color:", cols[["council led"]], "'><strong>Council-led</strong></span> facilities<br>in this Local Board")) +
    theme(
      legend.position = "none",
      plot.title = element_markdown(lineheight = 1.1, size = 16, colour = "#515555")
    ) 
}

facilities <- readRDS(fs::dir_ls(here::here("data/facilities_for_ltp.rds"))) |> 
  filter(local_board != "Great Barrier") |> 
  mutate(name = case_when(
    name %in% c("Albert Park Caretaker's Cottage", "Smiths Avenue Clubrooms", "Takaanini") ~ paste0(name, "*"),
    TRUE ~ name
  ))
  
```

## Introduction

Welcome to this one-page guide on in-scope Connected Communities facilities for the FY22 LTP metric quoted below:

>The percentage of art facilities, community centres and hire venues network that is community led

Use the navigation menu to the left to select your name, and then the sub-menu allows you to navigate to a Local Board of interest within your remit. There you will see the name of each in-scope facility within that Local Board, colour coded to indicate whether it is a Council-led or a community-led facility. An asterik (*) next to the facility indicates that it was not included in last year's data, but has been included this year.

Once you're satisfied with what is shown for each Local Board within your remit, be sure to return to the spreadsheet to mark that you have signed it off. If you have questions or instructions to modify the narrative, please provide these in the spreadsheet.

For any questions about this data please contact Lee Durbin in the Insights Team: <lee.durbin@aucklandcouncil.govt.nz>


```{r block_chart_template, eval=FALSE}
choose_facilities(chosen_lb) |>
  build_block_visual()
```


## **Kim**

```{r, child=c('kim.Rmd'), eval=TRUE}

```


## **Kevin**

```{r, child=c('kevin.Rmd'), eval=TRUE}

```


## **Darryl**

```{r, child=c('darryl.Rmd'), eval=TRUE}

```
